\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2.2cm, top=2.5cm, bottom=2.5cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{float}
\usepackage{fontenc}
\usepackage{lmodern}

% ── Colour palette ────────────────────────────────────────────────────────────
\definecolor{brand}{HTML}{1A4DFF}
\definecolor{dark}{HTML}{111111}
\definecolor{mid}{HTML}{2E3129}
\definecolor{light}{HTML}{F4F4F6}
\definecolor{rule}{HTML}{E0E0E0}

% ── Hyperref ─────────────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  linkcolor=brand,
  urlcolor=brand,
  pdftitle={Client Services Guide — Ujjwal Prakash},
  pdfauthor={Ujjwal Prakash},
}

% ── Section styling ───────────────────────────────────────────────────────────
\titleformat{\section}
  {\Large\bfseries\color{dark}}
  {}
  {0em}
  {}
  [\vspace{-0.3em}\color{brand}\rule{\linewidth}{1.5pt}\vspace{0.4em}]

\titleformat{\subsection}
  {\normalsize\bfseries\color{dark}}
  {}
  {0em}
  {}

\titlespacing*{\section}{0pt}{1.8em}{0.5em}
\titlespacing*{\subsection}{0pt}{1em}{0.2em}

% ── List styling ──────────────────────────────────────────────────────────────
\setlist[itemize]{leftmargin=1.4em, itemsep=0.15em, topsep=0.3em}
\setlist[enumerate]{leftmargin=1.4em, itemsep=0.15em, topsep=0.3em}

% ── Row colour helper ────────────────────────────────────────────────────────
\newcommand{\headerrow}{\rowcolor{brand!10}}

\begin{document}

% ── HEADER ───────────────────────────────────────────────────────────────────
\begin{center}
  {\fontsize{28}{32}\selectfont\bfseries\color{dark} Client Projects}\\[4pt]
  {\fontsize{28}{32}\selectfont\bfseries\color{brand} Services Guide}\\[12pt]
  {\small\color{mid} Ujjwal Prakash\ \ \textbullet\ \ Senior Software Engineer \& Team Lead\ \ \textbullet\ \ IIT Kanpur}\\[4pt]
  {\small\color{mid}
    \href{mailto:ujjwalprakash858@gmail.com}{ujjwalprakash858@gmail.com}\ \ \textbullet\ \ 
    \href{https://www.linkedin.com/in/ujjwal-prakash-036873336/}{LinkedIn}\ \ \textbullet\ \ 
    \href{https://github.com/ujjwalPrakash-spike}{GitHub}
  }
\end{center}

\vspace{0.5em}
\color{rule}\rule{\linewidth}{0.4pt}\color{dark}
\vspace{0.8em}

{\color{mid}\small
How I build software for clients. A transparent breakdown of my technical stack, architecture principles, engineering process, and what working with me actually looks like — so you can make an informed decision before we start.
}

\vspace{1em}

% ── 1. WHO I AM ──────────────────────────────────────────────────────────────
\section{Who I Am}

I am a Senior Software Engineer and Team Lead at IIT Kanpur, currently leading the development of the official IIT Kanpur Recruitment Automation System (RAS) — a production platform serving over \textbf{30,000+ students and 20,000+ active users}. I manage a team of 4 engineers across a 37,000+ line production codebase.

Beyond engineering, I am a peer-reviewed researcher. My deep learning work on ISRO's earth observation data was \textbf{accepted for an oral presentation at IEEE IGARSS 2026} — one of the most competitive geospatial intelligence conferences in the world.

I also teach full-stack engineering, with a \textbf{4.8/5.0 student rating}, which means I can communicate complex technical decisions in plain language — something clients consistently value.

% ── 2. WHAT I BUILD ──────────────────────────────────────────────────────────
\section{What I Build}

\subsection{Backend Systems}

I specialise in high-concurrency, production-grade backend systems. This includes REST and gRPC API design, authentication flows, database schema design, background job processing, and systems that need to handle thousands of concurrent users without degrading.

\begin{itemize}
  \item \textbf{Go (Golang)} — primary backend language for performance-critical services
  \item \textbf{TypeScript / Node.js} — APIs, microservices, BFF (Backend for Frontend) layers
  \item \textbf{PostgreSQL} — relational data modelling, query optimisation, indexing strategies
  \item \textbf{Redis} — caching, session management, pub-sub, distributed locks
  \item \textbf{Docker \& CI/CD} — containerised deployments, GitHub Actions pipelines
\end{itemize}

\subsection{Full-Stack Platforms}

When the project requires a complete product, I can deliver end-to-end:

\begin{itemize}
  \item \textbf{Next.js} — SSR/SSG, API routes, auth integration, performance-optimised frontend
  \item \textbf{React} — component-driven UI with TypeScript, state management, animation
  \item \textbf{Database-to-UI pipelines} — from schema design through to rendered data tables
\end{itemize}

\subsection{AI \& Research Integration}

With hands-on ML research experience (deep learning for satellite imagery, ISRO collaboration), I can integrate modern AI capabilities into products:

\begin{itemize}
  \item LLM API integration (OpenAI, Anthropic, Google)
  \item Computer vision pipelines for custom datasets
  \item Data processing and analytics backends
\end{itemize}

% ── 3. TECHNICAL STACK ───────────────────────────────────────────────────────
\section{Technical Stack}

\begin{tabularx}{\linewidth}{@{} l X @{}}
  \toprule
  \rowcolor{brand!8}
  \textbf{Layer} & \textbf{Technologies} \\
  \midrule
  \textbf{Languages}    & Go, TypeScript, Python, SQL \\
  \addlinespace[0.2em]
  \textbf{Backend}      & Go (net/http, Chi, Gin), Node.js, REST, gRPC \\
  \addlinespace[0.2em]
  \textbf{Frontend}     & Next.js 14/15, React, Tailwind CSS, Framer Motion \\
  \addlinespace[0.2em]
  \textbf{Databases}    & PostgreSQL, Redis, SQLite \\
  \addlinespace[0.2em]
  \textbf{DevOps}       & Docker, GitHub Actions, Nginx, Linux servers \\
  \addlinespace[0.2em]
  \textbf{AI/ML}        & PyTorch, OpenCV, Scikit-learn, LLM APIs \\
  \addlinespace[0.2em]
  \textbf{Tools}        & Git, Postman, pgAdmin, Figma (handoff) \\
  \bottomrule
\end{tabularx}

% ── 4. HOW I WORK ────────────────────────────────────────────────────────────
\section{How I Work — Engineering Process}

\subsection{Phase 1: Discovery (Days 1--3)}

Before writing a single line of code, I need to fully understand what you are building and why. This phase involves a structured conversation covering your users, scale expectations, existing systems, and non-negotiables (compliance, latency, budget).

Deliverable: a written scope document with agreed-upon architecture decisions, tech stack rationale, and a realistic timeline.

\subsection{Phase 2: Architecture \& Schema Design (Days 3--7)}

Good systems are designed before they are built. I produce:
\begin{itemize}
  \item Entity-relationship diagrams and database schema
  \item API contract (endpoints, request/response shapes, error codes)
  \item Sequence diagrams for critical user flows
  \item Deployment architecture diagram (services, external dependencies, data flow)
\end{itemize}

This phase is deliberately slow. Decisions made here are far cheaper to change than decisions made in production.

\subsection{Phase 3: Development (Variable)}

I follow a trunk-based development workflow with atomic commits and descriptive pull requests. Every feature ships with:
\begin{itemize}
  \item Unit and integration tests
  \item Clear inline documentation
  \item Migration scripts for any database changes
  \item A staging environment deployment before production
\end{itemize}

I send progress updates at every meaningful milestone — not just at the end.

\subsection{Phase 4: Testing \& Handoff}

Before marking work complete, the system passes:
\begin{itemize}
  \item Load testing at $2\times$ expected peak traffic
  \item Security review (auth, input validation, SQL injection checks)
  \item Documentation: README, API reference, deployment runbook
\end{itemize}

Handoff includes a walkthrough call and 14 days of post-launch support for critical bugs at no additional charge.

% ── 5. WHAT TO EXPECT ────────────────────────────────────────────────────────
\section{What You Can Expect From Me}

\begin{itemize}
  \item \textbf{Honest timelines.} I do not promise what I cannot deliver. If a scope is unrealistic, I say so before we begin.
  \item \textbf{Clear communication.} Written updates, not just verbal ones. Decision logs so you always know why something was built the way it was.
  \item \textbf{Production-first thinking.} Code that will survive real users, not just a demo environment. I have maintained a 99.9\% uptime system in production — I build with that standard.
  \item \textbf{No lock-in.} You own everything. Clean, documented code that any competent engineer can continue after me.
\end{itemize}

% ── 6. ENGAGEMENT TYPES ──────────────────────────────────────────────────────
\section{Engagement Types}

\begin{tabularx}{\linewidth}{@{} l l X @{}}
  \toprule
  \rowcolor{brand!8}
  \textbf{Type} & \textbf{Duration} & \textbf{Best For} \\
  \midrule
  \textbf{Project-based}   & 2--16 weeks  & Defined scope with clear deliverables \\
  \addlinespace[0.2em]
  \textbf{Advisory retainer} & Monthly      & Ongoing architecture review, code review, technical direction \\
  \addlinespace[0.2em]
  \textbf{Rescue mission}  & 1--4 weeks   & Existing codebase in trouble — performance, bugs, or security \\
  \addlinespace[0.2em]
  \textbf{Build to hand off} & 4--12 weeks & Full system built and documented for an in-house team to own \\
  \bottomrule
\end{tabularx}

% ── 7. NOT A FIT ─────────────────────────────────────────────────────────────
\section{When We Are Probably Not a Good Fit}

I want to be honest about this, because misaligned expectations waste everyone's time.

\begin{itemize}
  \item You need a resource who is available 24/7 and interruptible on demand
  \item The project has no defined problem — only a vague idea with no user validation
  \item You expect a fixed-price quote before any discovery conversation
  \item The timeline is ``as fast as possible'' with no flexibility
\end{itemize}

% ── 8. HOW TO START ──────────────────────────────────────────────────────────
\section{How to Start}

The first step is a 30-minute conversation — no pitch, no pressure. I want to understand your problem and tell you honestly whether I can help.

\begin{center}
  \vspace{0.5em}
  \large\bfseries
  \href{mailto:ujjwalprakash858@gmail.com}{ujjwalprakash858@gmail.com}
  \vspace{0.3em}
\end{center}

\vspace{0.5em}
\color{rule}\rule{\linewidth}{0.4pt}\color{dark}
\vspace{0.5em}

{\small\color{mid}
\textbf{Ujjwal Prakash} — Senior Software Engineer \& Team Lead, IIT Kanpur.
Promoted for leading a 30K+ user production system. IEEE IGARSS 2026 accepted researcher. 4.8/5.0 teaching rating.\\[4pt]
\href{https://www.linkedin.com/in/ujjwal-prakash-036873336/}{linkedin.com/in/ujjwal-prakash-036873336}\ \ \textbullet\ \ 
\href{https://github.com/ujjwalPrakash-spike}{github.com/ujjwalPrakash-spike}
}

\end{document}
